Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Separate final chapter into analysis and conclusions
Update todo
Conclusion headlines

@@

% Report, restructuring
% TODO: Improve connectivity between two first paragraphs in the abstract
% TODO: Merge section 3 with the background chapter
% TODO: Move talk about specific geodata to Implementation section
% TODO: Move 4.1 -> Evaluation/Methodology (new section)
% TODO: Overview at the beginning of each chapter
% TODO: Move conclusions to a new Part 2 of Results and Metrics
% TODO: New conclusions and future work section
% TODO: Make research questions even clearer

@@

\section{Scientific field study}

@@

Such procedural techniques have long been available.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.
For simple presentation in e.g. animation and videogames or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life, such models will be sufficient as long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
Many studies urban development have been done before that requred detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development
\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)}
and reducing noise.
\textbf{(Joon, Seo and Byung, 2011)}

It even turns out, by looking at such studies, that a lot of research in urban development require detailed morpological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morpological structures where a single feature, such as a city neighbourhood, can be examined from many different levels of perspective.
A neighbourhood can be analysed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Simlarily a road network can be analysed by looking at it either at its connectivity by viewing it a a simple 2D graph
But it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morpological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation, but it may even describe subtilities like building facades and distances between curbline and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
\textbf{(Stojanovski, 2019)}
For media applications, such morppological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.

>>>>

\chapter{Analysis}

@@

% Report, restructuring
% TODO: Summarize Analysis in Conclusions
% TODO: Overview at the beginning of each chapter

@@

\section{Data conclusions}

\section{Remaining challenges in city reproduction}

@@

\section{Using procedural methods}

Procedural techniques are, as mentioned, methods for reconstructing or creating 3D automatically, with minimal manual work required. Adding such techniques for content creation into the workflow of city reconstruction will increase the level of detail that is possible, while sacrificing accuracy to the real-world.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.
For simple presentation in e.g. animation and videogames or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life, such models will be sufficient as long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
Many studies urban development have been done before that requred detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development
\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)}
and reducing noise.
\textbf{(Joon, Seo and Byung, 2011)}

\section{Feasibility in the urban planning field}
By looking at such studies in urban development, one will discover that a lot of research in this field requires detailed morpological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morpological structures where a single feature, such as a city neighbourhood, can be examined from many different levels of perspective.
A neighbourhood can be analysed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Simlarily a road network can be analysed by looking at it either at its connectivity by viewing it a a simple 2D graph
But it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morpological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation, but it may even describe subtilities like building facades and distances between curbline and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
\textbf{(Stojanovski, 2019)}
For media applications, such morppological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.

\section{Final conclusions}
